He-Man: A domain specific language for lightweight concurrency

### 2012-03-11 paper/paper.tex
Add note about HTTP server.

To compare the ease of writing event based network applications, we
built simple echo servers using both He-Man and C. The C version was
written in as an event loop driven explicit state machine using the
He-Man runtime. The C version, which is fairly tightly written and
which uses the He-Man runtime in its capacity as a somewhat generic
event based IO framework, is 98 lines of source, according to
SLOCCount. It is fairly readable, but its structure is obscured by
being split into states and the need to explicitly handle read and
write returning \t{EAGAIN} and write returning short. The state
machine has a total of five states. The He-Man version is 33 lines
long and is a very clear representation of the control flow of each
individual thread. (Additionally, the He-Man library has 17 lines of
code implementing generic routines for simulating blocking IO using
nonblocking IO and wait.) The total line counts, however, somewhat
understate the difference between the versions, since the boilerplate
for setting up connections is about the same for both versions. When
just looking at the core read/write loop, the difference is much more
apparent: the C version is 38 lines of code, and the He-Man version is
5.

The generated code is substantially less tight than the C version,
although it is unlikely to be any slower in practice. It has 10 states
and is 240 lines of C.
%This could be reduced substantially by allowing
%conditionals outside of block tail position.

>>>>

To compare the ease of writing event based network applications, we
built simple echo servers using both He-Man and C. The C version was
written in as an event loop driven explicit state machine using the
He-Man runtime. The C version, which is fairly tightly written and
which uses the He-Man runtime in its capacity as a somewhat generic
event based IO framework, is 98 lines of source, according to
SLOCCount. It is fairly readable, but its structure is obscured by
being split into states and the need to explicitly handle read and
write returning \t{EAGAIN} and write returning short. The state
machine has a total of five states. The He-Man version is 33 lines
long and is a very clear representation of the control flow of each
individual thread. (Additionally, the He-Man library has 25 lines of
code implementing generic routines for simulating blocking IO using
nonblocking IO and wait.) The total line counts, however, somewhat
understate the difference between the versions, since the boilerplate
for setting up connections is about the same for both versions. When
just looking at the core read/write loop, the difference is much more
apparent: the C version is 38 lines of code, and the He-Man version is
5.

The generated code is substantially less tight than the C version,
although it is unlikely to be any slower in practice. It has 10 states
and is 240 lines of C. The echo server was able to handle 10,000
concurrent, occasionally transmitting, connections with no
problem. With 10,000 clients connected the echo server used about 40
MB of memory, which is almost entirely accounted for 4 KB buffer that
each connection maintained for I/O.
